Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2015-01-15 paper.tex
figure 3 is for NS, not MHD
also, add "conventional" in front of theory for reconnection, since
there is an alternate theory that does predict the correct time.

Figure \ref{fig:max_vort_cluster} shows the most intense event observed in the MHD dataset. The locations of maximum vorticity in the dataset were clustered
in this case in 4d using a friends-of-friends algorithm. It is interesting to note that the cluster containing the most intense event in the entire dataset develops
from nothing (i.e. it does not appear in the first few time-steps) and it takes less than the timespan stored in the database for it to develop. 
%The timespan stored is equal to about one large eddy turnover time. 
%It is not clear whether a different more intense event could emerge from an existing
%cluster if the timespan stored was larger. 
Figure \ref{fig:max_vort_cluster} also shows that most interactions between worms are not simple. 
There are several worms interacting in a complex way at the same time. Similar type of analysis and the fact that the entire time history of the simulation
is available in a database cluster, which provides built-in sophisticated analysis routines revealed flux-freezing breakdown in MHD turbulence \cite{Eyink},
showing why solar flares last minutes rather than the millions of years that theory would predict.

>>>>

Figure \ref{fig:max_vort_cluster} shows the most intense event observed in the forced isotropic turbulence dataset. The locations of maximum vorticity in the dataset were clustered
in this case in 4d using a friends-of-friends algorithm. It is interesting to note that the cluster containing the most intense event in the entire dataset develops
from nothing (i.e. it does not appear in the first few time-steps) and it takes less than the timespan stored in the database for it to develop. 
%The timespan stored is equal to about one large eddy turnover time. 
%It is not clear whether a different more intense event could emerge from an existing
%cluster if the timespan stored was larger. 
Figure \ref{fig:max_vort_cluster} also shows that most interactions between worms are not simple. 
There are several worms interacting in a complex way at the same time. Similar type of analysis and the fact that the entire time history of the simulation
is available in a database cluster, which provides built-in sophisticated analysis routines revealed flux-freezing breakdown in MHD turbulence \cite{Eyink},
showing why solar flares last minutes rather than the millions of years that conventional theory would predict.
